|

### 2024-08-09 doc/paper.qmd
EM1

3.	Calculate EM1, which is determined as the country’s median ratio of the firm-level standard deviations of operating income and operating cash flow. Both standard deviations are scaled by lagged total assets to control for differences in firm size:
$$
\text{EM1} = \text{Median}\left(\frac{\sigma(\text{Operating Income}_{it})}{\sigma(\text{Operating Cash Flow}_{it})}\right) \quad \text{scaled by lagged total assets}
$$

>>>>

3.	Calculate EM1, which is determined as the country’s median ratio of the firm-level standard deviations of operating income and operating cash flow. Both standard deviations are scaled by lagged total assets to control for differences in firm size:
$$
\text{EM1} = \text{Median}\left(\frac{\sigma(\text{Operating Income}_{it})}{\sigma(\text{Operating Cash Flow}_{it})}\right) \quad \text{both separately scaled by lagged total assets}
$$
